correlation_part2

### 2023-10-31 graphs_newt_snakes/correlation_part2.Rmd
making more plots

names(newt_info)[names(newt_info) == 'measurement'] <- 'newt_toxin'
newt_info$snake_res<-snake_info$measurement
newt_info$dif<-newt_info$snake_res-newt_info$newt_toxin
pattern<-"Newt_1.0e-08_0.005_Snake_1.0e-08_0.005_0"
scatter_pheno<-newt_info[which(newt_info$newt_snake_rep==pattern & newt_info$generation>14000 & newt_info$generation<15000 ),]
scatter_pheno<-newt_info[which(newt_info$newt_snake_rep==pattern & newt_info$generation==20981 ),]
#scatter_pheno[scatter_pheno == 0] <- NA
#scatter_pheno[scatter_pheno == 1] <- NA
ggplot(scatter_pheno)+
 ggtitle(paste0(" pattern ", pattern, " From ", min(scatter_pheno$generation), " gen to ", max(scatter_pheno$generation), " gen"))+
  geom_point(aes(y = newt_toxin, x = snake_res, color=generation), size = 3) 
  theme_bw()

>>>>

names(newt_info)[names(newt_info) == 'measurement'] <- 'newt_toxin'
newt_info$snake_res<-snake_info$measurement
newt_info$dif<-newt_info$snake_res-newt_info$newt_toxin
pattern<-"Newt_1.0e-08_0.005_Snake_1.0e-08_0.005_0"
scatter_pheno<-newt_info[which(newt_info$newt_snake_rep==pattern & newt_info$generation>14000 & newt_info$generation<15000 ),]
#scatter_pheno<-newt_info[which(newt_info$newt_snake_rep==pattern & newt_info$generation==20981 ),]
scatter_pheno[scatter_pheno == 0] <- NA
scatter_pheno[scatter_pheno == 1] <- NA
ggplot(scatter_pheno)+
 ggtitle(paste0(" pattern ", pattern, " From ", min(scatter_pheno$generation), " gen to ", max(scatter_pheno$generation), " gen"))+
  geom_point(aes(y = newt_toxin, x = snake_res, color=generation), size = 3) 
  theme_bw()
